Cronchbach's alpha and FAs on scales

### 2023-09-20 module2/factor analysis/module2PCAs.Rmd
lot of changes because I wasn't opening the project file.

---
title: "PCAs"
output: word_document

---

```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
  knitr::opts_chunk$set(warning = FALSE, message = FALSE)

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))

suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(DT))

suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(psych)) # psychometrics

@@

# reverse code for likert scale for variables for Kahan scale into numbers
mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                               . == "Somewhat disagree" ~ 2,
                                                               . == "Neither agree nor disagree" ~3,
                                                               . == "Somewhat agree" ~ 4,
                                                               . == "Strongly agree" ~ 5))) %>%

# code eco-pol scale variables into numbers
  mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG), funs(case_when(. == "Strongly disagree" ~ 1, 
                        . == "Somewhat disagree" ~ 2,
                        . == "Neither agree nor disagree" ~3,
                        . == "Somewhat agree" ~ 4,
                        . == "Strongly agree" ~ 5))) %>%

# reverse code eco-pol scale variables into numbers 
 mutate_at(vars(DECISIONCEN, INDUSTRYSMALL, ECONOMYLOCAL, ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 1, 
                                                                                                         . == "Somewhat disagree" ~ 2,
                                                                                                         . == "Neither agree nor disagree" ~3,
                                                                                                         . == "Somewhat agree" ~ 4,
                                                                                                         . == "Strongly agree" ~ 5)))
```

@@

- **K_IINTRFER**	The government interferes far too much in our everyday lives.
- **K_IPRIVACY**	The government should stop telling people how to live their lives.
- **K_SHARM**	    Sometimes the government needs to make laws that keep people from hurting themselves.
- **K_IPROTECT**	It’s not the government’s business to try to protect people from themselves.
- **K_SLIMCHOI**	The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.
- **K_SPROTECT**	The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.

@@

Cronbach's alpha test on the Kahan et al (2007) scale

@@

@@

KahanS <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_S", "K_I")))%>%
  na.omit()

#K_S items produce a strong alpha but not K_I

KahanI.alpha <- psych::alpha(KahanI)

KahanE <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_H", "K_E")))%>%
  na.omit()

KahanE.alpha <- psych::alpha(KahanE, check.keys = TRUE)

@@

Factor Analysis on Kahan et al (2007) scale: 2 factor spaces

```{r, echo=FALSE}

#factor analysis on Kahan scale: 2 factor spaces
Kahan <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_")))%>%
  na.omit()

Kahan.fa <- fa(Kahan, nfactors=2, scores=TRUE, rotate="varimax", fm="pa")
#print.psych(Kahan.fa, cut = 0.3, sort = TRUE)
#fa.diagram(Kahan.fa)

loadingskahan <- unclass(Kahan.fa$loadings)

loadingstablekahan <- cbind(loadingskahan)

twofakahan <- as_tibble(loadingstablekahan) %>%
add_column("Items" = c("The government interferes far too much in our everyday lives", 
"The government should stop telling people how to live their lives", 
"Sometimes the government needs to make laws that keep people from hurting themselves" , 
"It’s not the government’s business to try to protect people from themselves", 
"The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society", 
"The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals", 
"We have gone too far in pushing equal rights in this country",
"Nowadays it seems like there is just as much discrimination against upper castes as there is against Dalits",
"Discrimination against minorities is still a very serious problem in our society", 
"We need to dramatically reduce inequalities between the rich and the poor",
"Our society would be better off if the distribution of wealth was more equal",
"We need to dramatically reduce inequalities between men and women")) %>%
dplyr::select("Items",  PA1, PA2) %>%
  arrange(desc(PA1))

knitr::kable(twofakahan, digits = 2)

VarexplK <- unclass(Kahan.fa$Vaccounted)

knitr::kable(VarexplK, digits = 2)
```

Factor Analysis on Kahan et al (2007) scale: 4 factor spaces

```{r, echo=FALSE}
#factor analysis on Kahan scale: 4 factor spaces 
Kahan <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_")))%>%
  na.omit()

fourKahan.fa <- fa(Kahan, nfactors=4, scores=TRUE, rotate="varimax", fm="pa")
#print.psych(Kahan.fa, cut = 0.3, sort = TRUE)
#fa.diagram(Kahan.fa)

fourloadingskahan <- unclass(fourKahan.fa$loadings)

fourloadingstablekahan <- cbind(fourloadingskahan)

fourfakahan <- as_tibble(fourloadingstablekahan) %>%
add_column("Items" = c("The government interferes far too much in our everyday lives", 
"The government should stop telling people how to live their lives", 
"Sometimes the government needs to make laws that keep people from hurting themselves" , 
"It’s not the government’s business to try to protect people from themselves", 
"The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society", 
"The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals", 
"We have gone too far in pushing equal rights in this country",
"Nowadays it seems like there is just as much discrimination against upper castes as there is against Dalits",
"Discrimination against minorities is still a very serious problem in our society", 
"We need to dramatically reduce inequalities between the rich and the poor",
"Our society would be better off if the distribution of wealth was more equal",
"We need to dramatically reduce inequalities between men and women")) %>%
dplyr::select("Items",  PA1, PA2, PA3, PA4)%>%
  arrange(desc(PA1))

knitr::kable(fourfakahan, digits= 2)

VarexplK <- unclass(fourKahan.fa$Vaccounted)

knitr::kable(VarexplK, digits = 2)
```

**The economic -political values of the perceiver scale**

Cronbach's alpha test on the economic -political values of the perceiver

```{r, echo= FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
ecopolscalescores <- codedmodule2 %>%
 dplyr::select(starts_with(c("SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
  rowwise()%>%
  na.omit()#%>%
  #dplyr::mutate(Pro_decentralisation = mean(c_across("DECISIONDECEN":"DECISIONCEN")))%>%
   #dplyr::mutate(Pro_largescale = mean(c_across("INDUSTRYLARGE":"INDUSTRYSMALL")))%>%
   #dplyr::mutate(Pro_global = mean(c_across("ECONOMYGLOBAL":"ECONOMYLOCAL")))%>%
   #dplyr::mutate(Pro_ecogrowth = mean(c_across("ENVOVERDEV":"DEVOVERENV")))%>%
   #dplyr::mutate(Pro_private = mean(c_across("OWNERPVT":"OWNERREG")))%>%
  #dplyr::select(!c("DECISIONDECEN","DECISIONCEN", "INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL", "ECONOMYLOCAL","ENVOVERDEV",     "DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG"))

psych::alpha(ecopolscalescores, check.keys = TRUE)

Factor Analysis on the economic and political values scale: 2 factor spaces

```{r, echo=FALSE}

#factor analysis with 2, 4 and 6 factor spaces

ecopolscale.fa <- fa(ecopolscalescores, nfactors=2, scores=TRUE, rotate="varimax", fm="pa")
#print.psych(ecopolscale.fa, cut = 0.3, sort = TRUE)
#fa.diagram(ecopolscale.fa)

loadingsecopol <- unclass(ecopolscale.fa$loadings)

loadingstableecopol <- cbind(loadingsecopol)

twofaecopol <- as_tibble(loadingstableecopol) %>%
add_column("Items" = c("Local politicians shouldn't have to ask permission from the central government to implement policies",
 "Laws and policies would be implemented more smoothly if more power lay with the central government",
"It is good to have a strong leader who does not have to bother with elections", 
 "Experts, not the government, should make decisions according to what they think is best for the country" , 
"It is very important to have a democratic political system because it ensures that no individual leader has too much power" , 
"There should be a system governed by religious law" , 
"Large corporations are destroying the local industries in India and benefiting only a handful of people" , 
"Large scale industries are required for the development of the country that will benefit everyone" , 
"India would be better off if foreign companies didn't come to here" , 
"Foreign companies have led to a range of benefits for the Indian people and society", 
"Economic growth and creating jobs should be prioritized over environmental protection" , 
"Polluting industries that spoil the environment should be shut down even if it costs people their jobs", 
"All businesses and industries should be owned privately", 
"The government should own most large businesses and industries", 
"Regardless of ownership, the government should pass strong regulations and implement them", 
"There is too much red-tape and the government should not interfere with businesses and industries" , 
"A limit should be put to how much wealth a person can amass",
 "Rapid mechanization of work is taking away jobs from workers in this country"))%>%
dplyr::select("Items",PA1, PA2)%>%
arrange(desc(PA1))

knitr::kable(twofaecopol, digits= 2)

Varexplecopol <- unclass(ecopolscale.fa$Vaccounted)

knitr::kable(Varexplecopol, digits = 2)

Factor Analysis on the economic and political values scale: 4 factor spaces

```{r, echo=FALSE}
#factor analysis with 4 factor spaces

ecopolscale4.fa <- fa(ecopolscalescores, nfactors=4, scores=TRUE, rotate="varimax", fm="pa")
#print.psych(ecopolscale.fa, cut = 0.3, sort = TRUE)
#fa.diagram(ecopolscale.fa)

loadingsecopol4 <- unclass(ecopolscale4.fa$loadings)

loadingstableecopol4 <- cbind(loadingsecopol4)

faecopol4 <- as_tibble(loadingstableecopol4) %>%
add_column("Items" = c("Local politicians shouldn't have to ask permission from the central government to implement policies",
 "Laws and policies would be implemented more smoothly if more power lay with the central government",
"It is good to have a strong leader who does not have to bother with elections", 
 "Experts, not the government, should make decisions according to what they think is best for the country" , 
"It is very important to have a democratic political system because it ensures that no individual leader has too much power" , 
"There should be a system governed by religious law" , 
"Large corporations are destroying the local industries in India and benefiting only a handful of people" , 
"Large scale industries are required for the development of the country that will benefit everyone" , 
"India would be better off if foreign companies didn't come to here" , 
"Foreign companies have led to a range of benefits for the Indian people and society", 
"Economic growth and creating jobs should be prioritized over environmental protection" , 
"Polluting industries that spoil the environment should be shut down even if it costs people their jobs", 
"All businesses and industries should be owned privately", 
"The government should own most large businesses and industries", 
"Regardless of ownership, the government should pass strong regulations and implement them", 
"There is too much red-tape and the government should not interfere with businesses and industries" , 
"A limit should be put to how much wealth a person can amass",
 "Rapid mechanization of work is taking away jobs from workers in this country"))%>%
dplyr::select("Items",PA1, PA2, PA3, PA4) %>%
  arrange(desc(PA1))

knitr::kable(faecopol4, digits= 2)

Varexplecopol4 <- unclass(ecopolscale4.fa$Vaccounted)

knitr::kable(Varexplecopol4, digits = 2)

Factor Analysis on the economic and political values scale: 6 factor spaces

```{r, echo=FALSE}

ecopolscale6.fa <- fa(ecopolscalescores, nfactors=6, scores=TRUE, rotate="varimax", fm="pa")
#print.psych(ecopolscale.fa, cut = 0.3, sort = TRUE)
#fa.diagram(ecopolscale.fa)

loadingsecopol6 <- unclass(ecopolscale6.fa$loadings)

loadingstableecopol6 <- cbind(loadingsecopol6)

faecopol6 <- as_tibble(loadingstableecopol6) %>%
add_column("Items" = c("Local politicians shouldn't have to ask permission from the central government to implement policies",
 "Laws and policies would be implemented more smoothly if more power lay with the central government",
"It is good to have a strong leader who does not have to bother with elections", 
 "Experts, not the government, should make decisions according to what they think is best for the country" , 
"It is very important to have a democratic political system because it ensures that no individual leader has too much power" , 
"There should be a system governed by religious law" , 
"Large corporations are destroying the local industries in India and benefiting only a handful of people" , 
"Large scale industries are required for the development of the country that will benefit everyone" , 
"India would be better off if foreign companies didn't come to here" , 
"Foreign companies have led to a range of benefits for the Indian people and society", 
"Economic growth and creating jobs should be prioritized over environmental protection" , 
"Polluting industries that spoil the environment should be shut down even if it costs people their jobs", 
"All businesses and industries should be owned privately", 
"The government should own most large businesses and industries", 
"Regardless of ownership, the government should pass strong regulations and implement them", 
"There is too much red-tape and the government should not interfere with businesses and industries" , 
"A limit should be put to how much wealth a person can amass",
 "Rapid mechanization of work is taking away jobs from workers in this country"))%>%
dplyr::select("Items",PA1, PA2, PA3, PA4, PA5, PA6) %>%
  arrange(desc(PA1))

knitr::kable(faecopol6, digits= 2)

Varexplecopol6 <- unclass(ecopolscale6.fa$Vaccounted)

knitr::kable(Varexplecopol6, digits = 2)
```

**Economic and Political characteristics of the energy technology scale -  Solar Energy and rooftop solar energy**

- **DISPLACESOLAR**	 Solar energy is leading to displacement of people from their land
- **POLLUTESOLAR**	 Solar energy increases pollution of air/water/land
- **HEALTHSOLAR**	   Solar energy poses a great risk to the health of people living around it
- **JOBSSOLAR**	     Solar energy will bring jobs to the local community
- **BEAUTYSOLAR**	   Solar energy spoils the natural beauty of the landscape
- **PRIDESOLAR**	   I would be proud if my community used solar energy
- **NPRIDESOLAR**	   Solar energy is a mark of pride for our nation
- **DEVSOLAR**	     Solar energy pushes forward the country's development
- **PROSPERSOLAR**	 Solar energy brings economic prosperity to the surrounding regions
- **RELYSOLAR**	     I don't like the idea that I have to rely on the government for electricity from (large scale) solar energy

Cronbach's alpha test on the Eco-Pol characteristics of the technology -  Solar Energy

@@

Solar <- codedmodule2 %>%
dplyr::select("DISPLACESOLAR":"RELYSOLAR") %>%
dplyr::rename("Solar energy is leading to displacement of people from their land" = "DISPLACESOLAR") %>%
dplyr::rename("Solar energy increases pollution of air/water/land" = "POLLUTESOLAR")%>%
dplyr::rename("Solar energy poses a great risk to the health of people living around it" = "HEALTHSOLAR")%>%
dplyr::rename("Solar energy will bring jobs to the local community" = "JOBSSOLAR")%>%
dplyr::rename("Solar energy spoils the natural beauty of the landscape" = "BEAUTYSOLAR")%>%
dplyr::rename("I would be proud if my community used solar energy" = "PRIDESOLAR")%>%
dplyr::rename("Solar energy is a mark of pride for our nation" = "NPRIDESOLAR") %>%
dplyr::rename("Solar energy pushes forward the country's development" = "DEVSOLAR")%>%
dplyr::rename("Solar energy brings economic prosperity to the surrounding regions" = "PROSPERSOLAR")%>%
dplyr::rename("I don't like the idea that I have to rely on the government for electricity from (large scale solar energy)" = "RELYSOLAR")%>%
  na.omit()

psych::alpha(Solar, check.keys = TRUE)

@@

Factor Analysis on the eco- pol characteristics of the technology, Solar Energy : 2 factor spaces

```{r, echo=FALSE}

#factor analysis with 2 factor spaces

solar.fa <- fa(Solar, nfactors=2, scores=TRUE, rotate="varimax", fm="pa")
#print.psych(solar.fa, cut = 0.4, sort = TRUE)
#fa.diagram(solar.fa)

loadingssolar <- unclass(solar.fa$loadings)

loadingstablesolar <- cbind(loadingssolar)

fasolar <- as_tibble(loadingstablesolar) %>%
add_column("Items" = c("Solar energy is leading to displacement of people from their land",
"Solar energy increases pollution of air/water/land",
"Solar energy poses a great risk to the health of people living around it",
"Solar energy will bring jobs to the local community",
"Solar energy spoils the natural beauty of the landscape",
"I would be proud if my community used solar energy",
"Solar energy is a mark of pride for our nation",
"Solar energy pushes forward the country's development",
"Solar energy brings economic prosperity to the surrounding regions",
"I don't like the idea that I have to rely on the government for electricity from (large scale) solar energy"))%>%
dplyr::select("Items",PA1, PA2)%>%
arrange(desc(PA1))

knitr::kable(fasolar, digits= 2)

Varexplsolar <- unclass(solar.fa$Vaccounted)

knitr::kable(Varexplsolar, digits = 2)
```

Factor Analysis on the eco- pol characteristics of the technology, Solar Energy : 4 factor spaces

```{r, echo=FALSE}

#factor analysis with  4 a factor spaces

solar4.fa <- fa(Solar, nfactors=4, scores=TRUE, rotate="varimax", fm="pa")
#print.psych(solar.fa, cut = 0.4, sort = TRUE)
#fa.diagram(solar.fa)

loadingssolar4 <- unclass(solar4.fa$loadings)

loadingstablesolar4 <- cbind(loadingssolar4)

fasolar4 <- as_tibble(loadingstablesolar4) %>%
add_column("Items" = c("Solar energy is leading to displacement of people from their land",
"Solar energy increases pollution of air/water/land",
"Solar energy poses a great risk to the health of people living around it",
"Solar energy will bring jobs to the local community",
"Solar energy spoils the natural beauty of the landscape",
"I would be proud if my community used solar energy",
"Solar energy is a mark of pride for our nation",
"Solar energy pushes forward the country's development",
"Solar energy brings economic prosperity to the surrounding regions",
"I don't like the idea that I have to rely on the government for electricity from (large scale) solar energy"))%>%
dplyr::select("Items",PA1, PA2, PA3, PA4) %>%
  arrange(desc(PA1))

knitr::kable(fasolar4, digits= 2)

Varexplsolar4 <- unclass(solar4.fa$Vaccounted)

knitr::kable(Varexplsolar4, digits = 2)
```

```{r, echo=FALSE}
ROOFS<- codedmodule2 %>%
 dplyr::select("DISPLACEROOFS":"RELYROOFS")

psych::alpha(ROOFS, check.keys = TRUE)

@@

```{r, echo=FALSE}
#factor analysis with 2, 4 and 6 factor spaces

roofs.fa <- fa(ROOFS, nfactors=2, scores=TRUE, rotate="varimax", fm="pa")
#print.psych(roofs.fa, cut = 0.4, sort = TRUE)
#fa.diagram(roofs.fa)

loadingsroofs <- unclass(roofs.fa$loadings)

loadingstableroofs <- cbind(loadingsroofs)

faroofs <- as_tibble(loadingstableroofs) %>%
add_column("Items" = c("Rooftop solar is leading to displacement of people from their land",
"Rooftop solar increases pollution of air/water/land", 
"Rooftop solar poses a great risk to the health of people living around it",
"Rooftop solar will bring jobs to the local community",
"Rooftop solar spoils the natural beauty of the landscape" , 
"I would be proud if my community used Rooftop solar" , 
"Rooftop solar is a mark of pride for our nation", 
"Rooftop solar pushes forward the country's development" , 
"Rooftop solar brings economic prosperity to the surrounding regions" , 
"I don't like the idea that I have to rely on the government for electricity from (large scale) Rooftop solar")) %>%
dplyr::select("Items",  PA1, PA2)%>%
  arrange(desc(PA1))

knitr::kable(faroofs, digits = 2)

Varexplroofs <- unclass(roofs.fa$Vaccounted)

knitr::kable(Varexplroofs, digits = 2)

@@

>>>>

---
title: "Cronchbach's alpha and FAs on scales"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    keep_tex: yes
  header-includes:
  - \usepackage{dcolumn}
  - \usepackage{array}
  keep_md: yes
---

```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
  knitr::opts_chunk$set(warning = FALSE, message = FALSE)
suppressPackageStartupMessages(library(lavaan))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(psych)) # psychometrics

@@

# reverse code for likert scale for variables for Kahan scale into numbers
mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                               . == "Somewhat disagree" ~ 4,
                                                               . == "Neither agree nor disagree" ~3,
                                                               . == "Somewhat agree" ~ 2,
                                                               . == "Strongly agree" ~ 1))) %>%

# code eco-pol scale variables into numbers
  mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYSMALL,ECONOMYLOCAL,ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 1, 
                        . == "Somewhat disagree" ~ 2,
                        . == "Neither agree nor disagree" ~3,
                        . == "Somewhat agree" ~ 4,
                        . == "Strongly agree" ~ 5))) %>%

# reverse code eco-pol scale variables into numbers 
 mutate_at(vars(DECISIONCEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                                                                         . == "Somewhat disagree" ~ 4,
                                                                                                         . == "Neither agree nor disagree" ~3,
                                                                                                         . == "Somewhat agree" ~ 2,
                                                                                                         . == "Strongly agree" ~ 1)))
```
\newpage

# Kahan et al (2007) scale

## Cronbach's alpha test on the Kahan et al (2007) scale

@@

- **K_IINTRFER**	The government interferes far too much in our everyday lives.
- **K_IPRIVACY**	The government should stop telling people how to live their lives.
- **K_IPROTECT**	It’s not the government’s business to try to protect people from themselves.
- **K_SHARM**	    Sometimes the government needs to make laws that keep people from hurting themselves.
- **K_SLIMCHOI**	The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.
- **K_SPROTECT**	The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.

@@

KahanI weak alpha = 0.29, KahanS strong alpha = 0.71
Hierarchy -Egalitarianism strong alpha = 0.71
reasons for this could be that the individualism items are not well adapted to the Indian population 
final items alpha =  0.75

@@

#cronbach's alpha for the entire Kahan scale

Kahan <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_S", "K_I", "K_H", "K_E")))%>%
  na.omit()

Kahan.alpha <- psych::alpha(Kahan, check.keys = TRUE)

#summary(Kahan.alpha)

#cronbach's alpha for Individualism - Communitarinism scale

KahanSI <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_S", "K_I")))%>%
  na.omit()

KahanSI.alpha <- psych::alpha(KahanSI, check.keys = TRUE) #Alpha = 0.49

#summary(KahanSI.alpha)

KahanS <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_S")))%>%
  na.omit()

KahanI.alpha <- psych::alpha(KahanI, check.keys = TRUE)

# KahanI weak alpha = 0.29, KahanS strong alpha = 0.71
# reasons for this could be that the individualism items are not well adapted to the Indian population

KahanHE <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_H", "K_E")))%>%
  na.omit()

KahanHE.alpha <- psych::alpha(KahanHE, check.keys = TRUE)

#summary(KahanHE.alpha)

Kahanfas <- codedmodule2 %>%
  dplyr::select(K_SLIMCHOI, K_SPROTECT, K_SHARM, K_HEQUAL, K_ERADEQ1, K_EWEALTH, K_ERADEQ2)%>%
  na.omit()

Kahanfas.alpha <- psych::alpha(Kahanfas, check.keys = TRUE)

#summary(Kahanfas.alpha)
#Alpha 0.75

# Hierarchy -Egalitarianism strong alpha = 0.71

\newpage

# CFA on the Kahan scale

Since this a well used scale with theoretical basis for factor distinctions and there are also previous studies that used the same scale I did CFA not exploratory FA. 
```{r, echo=FALSE}

# CFA for Kahan scale. We shouldn't do FA here since this a well used scale with theoretical basis for factor distinctions and there are also previous studies that used the same scale

Kahan <- codedmodule2 %>%
  dplyr::select(starts_with(c("K_")))%>%
  na.omit()

Kahan_fas <- '
  KahanS =~ K_SHARM + K_SLIMCHOI + K_SPROTECT 
  KahanH =~ K_ERADEQ1 + K_EWEALTH + K_ERADEQ2
'

# Run CFA with standardization all method - gives standardized loadings 
# The factors are assumed to be correlated

Kahan_cfa <- cfa(Kahan_fas, data = Kahan, std.lv = TRUE)

# Print the summary of the CFA results, including fit measures
summary(Kahan_cfa, fit.measure= TRUE, standardized = TRUE)

# RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit and greater than 0.10 is poor fit 
# CFI - greater than 0.90 or 0.95 indicates good fit
#TFI - CFI>TFI >0.90 - indicates good fit

# after having removed a few variables that had very low loading, the model is now a good fit, we have two latent variables - Hierarchy- egalitarian and Communitarian. Again we see that individualistic variables just don't fit here.

# creating table of factor scores

Kahan_scores <- predict(Kahan_cfa, newdata = Kahan)

Kahan_Kscores <- cbind(Kahan, Kahan_scores)

```
\newpage

# Eco-pol value scale

**Scale 1 : The economic -political values of the perceiver**

## Cronbach's Alpha Test on Scale 1: Economic -Political Values of the Perceiver

```{r, echo= FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
ecopolscalescores <- codedmodule2 %>%
 dplyr::select(starts_with(c("SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
  na.omit()#%>%
  #dplyr::mutate(Pro_decentralisation = mean(c_across("DECISIONDECEN":"DECISIONCEN")))%>%
   #dplyr::mutate(Pro_largescale = mean(c_across("INDUSTRYLARGE":"INDUSTRYSMALL")))%>%
   #dplyr::mutate(Pro_global = mean(c_across("ECONOMYGLOBAL":"ECONOMYLOCAL")))%>%
   #dplyr::mutate(Pro_ecogrowth = mean(c_across("ENVOVERDEV":"DEVOVERENV")))%>%
   #dplyr::mutate(Pro_private = mean(c_across("OWNERPVT":"OWNERREG")))%>%
  #dplyr::select(!c("DECISIONDECEN","DECISIONCEN", "INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL", "ECONOMYLOCAL","ENVOVERDEV",     "DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG"))

@@

ecopol_alpha <- psych::alpha(ecopolscalescores, check.keys = TRUE)

summary(ecopol_alpha)

# Alpha for eco-pol values scale is good at 0.76- the scale has good inner consistency.

@@

\newpage

**Scale 2 : Economic and Political characteristics of the energy technology scale -  Nuclear energy**

- **DISPLACENUCLER** Nuclear energy is leading to displacement of people from their land
- **POLLUTENUCLEAR** Nuclear energy increases pollution of air/water/land
- **HEALTHNUCLEAR**	 Nuclear energy poses a great risk to the health of people living around it
- **JOBSNUCLEAR**	   Nuclear energy will bring jobs to the local community
- **BEAUTYNUCLEAR**	 Nuclear energy spoils the natural beauty of the landscape
- **PRIDENUCLEAR**	 I would be proud if my community used nuclear energy
- **NPRIDENUCLEAR**	 Nuclear energy is a mark of pride for our nation
- **DEVNUCLEAR**	   Nuclear energy pushes forward the country's development
- **PROSPERNUCLEAR** Nuclear energy brings economic prosperity to the surrounding regions
- **RELYNUCLEAR**	   I don't like the idea that I have to rely on the government for electricity from nuclear energy

## Cronbach's alpha test on Scale 2 : Eco-Pol Characteristics of the Technology -  Nuclear Energy

@@

Nuclear <- codedmodule2 %>%
dplyr::select("DISPLACENUCLEAR":"RELYNUCLEAR") %>%
dplyr::rename("Nuclear energy is leading to displacement of people from their land" = "DISPLACENUCLEAR") %>%
dplyr::rename("Nuclear energy increases pollution of air/water/land" = "POLLUTENUCLEAR")%>%
dplyr::rename("Nuclear energy poses a great risk to the health of people living around it" = "HEALTHNUCLEAR")%>%
dplyr::rename("Nuclear energy will bring jobs to the local community" = "JOBSNUCLEAR")%>%
dplyr::rename("Nuclear energy spoils the natural beauty of the landscape" = "BEAUTYNUCLEAR")%>%
dplyr::rename("I would be proud if my community used solar nuclear" = "PRIDENUCLEAR")%>%
dplyr::rename("Nuclear energy is a mark of pride for our nation" = "NPRIDENUCLEAR") %>%
dplyr::rename("Nuclear energy pushes forward the country's development" = "DEVNUCLEAR")%>%
dplyr::rename("Nuclear energy brings economic prosperity to the surrounding regions" = "PROSPERNUCLEAR")%>%
dplyr::rename("I don't like the idea that I have to rely on the government for electricity from (large scale nuclear energy)" = "RELYNUCLEAR")%>%
  na.omit()

nuclear_alpha <- psych::alpha(Nuclear, check.keys = TRUE)

summary(nuclear_alpha)

# std.alpha 0.68 - not very good

@@

## Cronbach's Alpha Test on the Combined Scale.

```{r, echo = FALSE}

# we combined both the scales, since we are interested in eco-pol factors at large - values of the perceiver and the values perceived in an energy technology.Here I have removed the variables on systems of government.

ecopolall <- codedmodule2 %>%
        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR", "SYSTEMDEMO")%>%
  na.omit()#%>%
  #dplyr::mutate(Pro_decentralisation = mean(c_across("DECISIONDECEN":"DECISIONCEN")))%>%
   #dplyr::mutate(Pro_largescale = mean(c_across("INDUSTRYLARGE":"INDUSTRYSMALL")))%>%
  #dplyr::select(!c("DECISIONDECEN","DECISIONCEN", "INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL", "ECONOMYLOCAL","ENVOVERDEV",     "DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG"))

ecopolall_alpha <- psych::alpha(ecopolall, check.keys = TRUE)

summary(ecopolall_alpha)

# when we combine both the scales the alpha is high at 0.785 (almost 0.8)

@@

\newpage

# FA on All Ecopol Variables (except systems of governance)

## Two factor solution : MR1 people centered development and MR2 nationalist development

**MR1 People Centered Development: Pdevelop**

HEALTHNUCLEAR	-  Nuclear energy poses a great risk to the health of people living around it.

BEAUTYNUCLEAR	-  Nuclear energy spoils the natural beauty of the landscape.

MECHANISATION	-  Rapid mechanization of work is taking away jobs from workers in this country.

INDUSTRYSMALL	-  Large corporations are destroying the local industries in India and benefiting only a handful of people.

DISPLACENUCLEAR- Nuclear energy is leading to displacement of people from their land.

POLLUTENUCLEAR-  Nuclear energy increases pollution of air/water/land.

OWNERREG-        Regardless of ownership, the government should pass strong regulations and implement them.

**MR2 Nationalist Development: Ndevelop**

DEVNUCLEAR	-  Nuclear energy pushes forward the country's development.

PRIDENUCLEAR-  I would be proud if my community used nuclear energy.

NPRIDENUCLEAR- Nuclear energy is a mark of pride for our nation.

PROSPERNUCLEAR-Nuclear energy brings economic prosperity to the surrounding regions.

INDUSTRYLARGE- Large scale industries are required for the development of the country that will benefit everyone.

```{r, echo = FALSE}
# FA on all ecopol variables except systems of governance

#ecopolall_cor <- cor(ecopolall)
#PCA24 <- principal(ecopolall, nfactors = 24, rotate = "none") # no rotation to start with.

#print(PCA24)

#PCA24$loadings

#fa.parallel(ecopolall_cor)

#PCA2 <- principal(ecopolall, nfactors = 2, rotate = "none") # no rotation to start with.

#print(PCA2)

#PCA2$loadings

# this suggests 2 factors if we go by FA or 8 by PCA. let's try both and see how they look conceptually

ecopolall2.fa <- fa(ecopolall, nfactors = 2, rotate = "varimax")

print.psych(ecopolall2.fa, cut = 0.50, sort = TRUE)

#fa.diagram(ecopolall2.fa)

#cor(ecopolall)

# So I am going to extract factor scores and bind them to the dataset

ecopolall_scores <- psych::factor.scores(ecopolall, ecopolall2.fa)

# The factor scores will be stored in the scores element of the returned list
scores1 <- ecopolall_scores$scores

@@

\newpage

# FA on Scale 1 - only eco-pol values of the perceiver scale.
